Verifying Demonstrations

### 2017-09-27 properties.tex
Moves implementation specifics from properties to protocol
WIP on #30, #29, #23

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.
This is fine, since we do not want to catch any cheater, we just do not want to
count them more than once.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Voting: different alternatives when participating.
      \item Protesting: participation implies the alternative.
    \end{itemize}
  \end{remark}

  \pause{}

  \begin{idea}[Proof privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.

        \pause{}

      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
  \begin{remark}
    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
    signatures are linked with high probability.
  \end{remark}

  \begin{question}
    Can we link a verified key to a unique ring signature key?
  \end{question}

  \pause{}

  \begin{question}
    How to submit the proofs to the system?
  \end{question}
\end{frame}

@@

Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
Alice has created one of the proofs.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item The proof itself is a sort of receipt.

        \pause{}

      \item If Eve compromises Alice's device, she can use it to verify that 
        she participated.

        \pause{}

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.
    \end{itemize}
  \end{remark}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.

        \pause{}

      \item E.g.\ a short-term and a long-term credential, then Alice can 
        drop the short-term credential.

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
}

  \pause{}

  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
\end{frame}

Say that Alice submits her proof and stores the hash of the head of the 
\ac{tposet} after her proof is included.
Now she can remove her proof and just keep the hash to verify that her proof is 
still there.
She can also remove her signature key, so that Eve cannot use it to reproduce 
the signature using the same inputs.

>>>>

\begin{frame}
\begin{definition}[Proof indistinguishability]
  \dots
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Receipt freeness/deniability]
  \dots
\end{definition}
\end{frame}

### 2017-09-27 protocol.tex
Moves implementation specifics from properties to protocol
WIP on #30, #29, #23

>>>>

\subsubsection{Participation-proof privacy}

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.
This is fine, since we do not want to catch any cheater, we just do not want to
count them more than once.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Voting: different alternatives when participating.
      \item Protesting: participation implies the alternative.
    \end{itemize}
  \end{remark}

  \begin{idea}[Proof privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.

      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
  \begin{remark}
    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
    signatures are linked with high probability.
  \end{remark}

  \begin{question}
    Can we link a verified key to a unique ring signature key?
  \end{question}

  \begin{question}
    How to submit the proofs to the system?
  \end{question}
\end{frame}

\subsubsection{Receipt freeness}

Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
Alice has created one of the proofs.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item The proof itself is a sort of receipt.

      \item If Eve compromises Alice's device, she can use it to verify that 
        she participated.

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.
    \end{itemize}
  \end{remark}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.

      \item E.g.\ a short-term and a long-term credential, then Alice can 
        drop the short-term credential.

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
}

  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
\end{frame}

Say that Alice submits her proof and stores the hash of the head of the 
\ac{tposet} after her proof is included.
Now she can remove her proof and just keep the hash to verify that her proof is 
still there.
She can also remove her signature key, so that Eve cannot use it to reproduce 
the signature using the same inputs.
